---
title: "Homework 6"
output: github_document
---

```{r setup}
library(tidyverse)
library(viridis)

library(modelr)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE, 
  fig.width = 8, 
  fig.height = 6, 
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "virids"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

Importing `birthweigth_df` data set

```{r}
birthweight_df = read_csv("./data/birthweight.csv")
```

Cleaning dataset

* `frace` = "unknown" (9) to missing (n/a)
* `malform` changed from `numeric` to `factor`

## any other data cleaning to do???
* no other missing values
* most variables continuous - keep as `numeric`

```{r}
birthweight_df  = 
  birthweight_df  %>% 
  mutate(frace = ifelse(is.na(frace), 9, frace),
         frace = factor(frace, levels = c("1", "2", "3", "4", "8"),
                  labels = c("white", "black", "asian", "puerto rican", "other")), 
        mrace = factor(mrace, levels = c("1", "2", "3", "4", "8"), labels = c("white", "black", "asian", "puerto rican", "other")),
         malform = as.factor(malform),
         babysex = factor(babysex, levels = c("1", "2"), labels = c("male", "female"))
    )
```

### Regression model proposal 

Previous research shows that many of the variables in this data set are associated with birth weight. In my proposed model I am looking to combine 2 variables, 2 biological (`babysex` and `delwt`) and one environmental predictor (`smoken`) as well as the interactions as a model of birth weight. 

### COME BACK TO THIS MODEL 

```{r}
my_fit = lm(bwt ~ delwt * babysex + smoken * babysex, data = birthweight_df)

broom::tidy(my_fit)
```

Plotting residuals against fitted values 

```{r}
birthweight_df %>% 
  modelr::add_residuals(my_fit) %>% 
  modelr::add_predictions(my_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()
```

Comparing to other models

```{r}
main_effects = 
  lm(bwt ~ blength + gaweeks, data = birthweight_df)

interaction = 
  lm(bwt ~ bhead * blength * babysex, data = birthweight_df)

broom::tidy(main_effects)
broom::tidy(interaction)
```

Comparing models with cross validation 

```{r}

cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

Fitting models and extracting RSME

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    my_fit = map(.x = train, ~lm(bwt ~ delwt * babysex + smoken * babysex, data = .x)),
    main_effects = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    interaction = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_my_fit = map2_dbl(.x = my_fit, .y = test, ~rmse(model = .x, data = .y)),
    rmse_main_effects = map2_dbl(.x = main_effects, .y = test, ~rmse(model = .x, data = .y)),
    rmse_interaction = map2_dbl(.x = interaction, .y = test, ~rmse(model = .x, data = .y))
  )
```

RMSE distributions

### rmse values are way too high 

```{r}
cv_df %>% 
  select(.id, starts_with("rmse")) %>% 
  pivot_longer(
    rmse_my_fit:rmse_interaction,
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_boxplot()
```

From this output, I would use the `interaction` model because it shows the distribution of RMSE scores around the lowest value. 

# Problem 2 

Downloading 2017 Central Park weather data 

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


Looking at the association between `tmax` (response) and `tmin` (predictor)

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

linear model:
```{r}
cp_linear = lm(tmax ~ tmin, data = weather_df)

broom::tidy(cp_linear)
```


* Checking to see if bootstrap is working on n = 10

* manipulating to get log(b0*b1)

```{r}
weather_bootstrap_results = 
  weather_df %>% 
  bootstrap(n = 10, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)


weather_bootstrap_results %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  rename(
    b0 = "(Intercept)", 
    b1 = "tmin"
  ) %>% 
  mutate(
    log_product = log(b0 * b1))
                  
```


Bootstrap check (n = 10)

* Broom::glance to get r-squred

```{r}
CP_bootstrap_rtest = 
  weather_df %>%  
  bootstrap(n = 10, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::glance)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)
```

Bootstrapping: sample = 5000 

```{r}
CP_bootstrap_results = 
  weather_df %>%  
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)



CP_bootstrap_r = 
  weather_df %>%  
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(tmax ~ tmin, data = .x)), 
    results = map(models, broom::glance)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)
```


Plotting distribution of estimates from bootstrap results 
```{r}
ggplot_tmin_estimate =
  CP_bootstrap_results %>% 
  filter(term == "tmin") %>% 
  ggplot(aes(estimate)) +
  geom_density()
```


Plotting distribution of r-squared results 

```{r}
ggplot_r_estimate =
  CP_bootstrap_r %>% 
  ggplot(aes(r.squared)) +
  geom_density()
```

Plotting distribution of log(b0*b1)

```{r}
ggplot_log_estimate =
  CP_bootstrap_results %>% 
    select(strap_number, term, estimate) %>% 
    pivot_wider(
      names_from = "term",
      values_from = "estimate"
    ) %>% 
    rename(
      b0 = "(Intercept)", 
      b1 = "tmin"
    ) %>% 
    mutate(
      log_product = log(b0 * b1)) %>% 
    ggplot(aes(log_product)) +
    geom_density()

```



Construct a bootstrap CI - bootstrap CI




